MSDS6371Project

### 2020-11-22 MSDS6371Project.Rmd
update rmd

temp = variables.used %>% drop_na()
```

### Stepwise Selection
```{r}
set.seed(11)
train.control <- trainControl(method = "cv", number = 10)
step.model = train(lSalePrice~.-Id, data=variables.used,
                   method="lmStepAIC",
                   trControl = train.control,
                   trace=FALSE)
step.model$results
step.model$finalModel
summary(step.model$finalModel)
print(step.model)
exp(0.1494448)
```

@@

>>>>

### Stepwise Selection
```{r}
set.seed(11)
train.control <- trainControl(method = "cv", number = 10)
step.model = train(lSalePrice~.-Id, data=variables.used,
                   method="lmStepAIC",
                   trControl = train.control,
                   trace=FALSE)
step.model$results
step.model$finalModel
summary(step.model$finalModel)
print(step.model)
# RMSE = 0.1494448 by 10 fold internal cross-validation
exp(0.1494448)
ols_plot_resid_stand(step.model$finalModel)
ols_plot_cooksd_bar(step.model$finalModel)
```

@@

### Forward Selection - Kaggle Score 0.15432
```{r}
set.seed(115)
#create forward fit model

#write a program to pretict 5 different combination to test forward selection model
iterations = 5
splitPerc = 0.9
total_RMSE = 0
for(i in 1:iterations){
  print(i)
  trainIndices = sample(1:dim(variables.used)[1],round(splitPerc * dim(variables.used)[1]))
  train = variables.used[trainIndices,]
  test = variables.used[-trainIndices,]
  forward_fit = lm(lSalePrice~.-Id,data=train)
  forward.model = ols_step_forward_aic(forward_fit,penter=0.15)
  prediction = predict(forward.model$model,test)
  squared_MSPE = mean((test$lSalePrice - prediction)^2)
  temp_RMSE = sqrt(squared_MSPE)
  total_RMSE = total_RMSE+temp_RMSE
}
#total RMSE = 0.1235978... RMSE = 839.29 under original SalePrice scale
total_RMSE/iterations

#Build model with full dataset for fitting
forward_fit = lm(lSalePrice~.-Id,data=variables.used)
forward.model = ols_step_forward_aic(forward_fit,penter=0.15)
forward.model$model
forward.model
ols_plot_resid_stand(forward.model$model)
ols_plot_cooksd_bar(forward.model$model)
plot(forward.model$model)

testVariable$lSalePriceForward = predict(forward.model$model,testVariable)
testVariable$SalePrice = exp(testVariable$lSalePriceForward)
result.forward = testVariable %>% dplyr::select(Id,SalePrice)
write.csv(result.forward,"Forward_Prediction_Miller_YU_2.csv",row.names = FALSE)

#Try Mass Library Forward model
forward.model2 = stepAIC(forward_fit,direction="forward")
forward.model2$model

### Backward Selection - Kaggle Score 0.15432
```{r}
set.seed(112)
#create forward fit model

#write a program to pretict 5 different combination to test forward selection model
iterations = 5
splitPerc = 0.95
total_RMSE = 0
for(i in 1:iterations){
  print(i)
  trainIndices = sample(1:dim(variables.used)[1],round(splitPerc * dim(variables.used)[1]))
  train = variables.used[trainIndices,]
  test = variables.used[-trainIndices,]
  backward_fit = lm(lSalePrice~.-Id,data=train)
  backward.model = ols_step_backward_aic(backward_fit)
  prediction = predict(backward.model$model,test)
  squared_MSPE = mean((test$lSalePrice - prediction)^2)
  temp_RMSE = sqrt(squared_MSPE)
  total_RMSE = total_RMSE+temp_RMSE
}
#CV Press Estimate = 0.1481379
total_RMSE/iterations

#Build model with full dataset for fitting
backward_fit = lm(lSalePrice~.-Id,data=variables.used)
backward.model = ols_step_backward_aic(backward_fit)
backward.model$model
backward.model
ols_plot_resid_stand(backward.model$model)
ols_plot_cooksd_bar(backward.model$model)
plot(backward.model$model)

testVariable$lSalePriceBackward = predict(backward.model$model,testVariable)
testVariable$SalePrice = exp(testVariable$lSalePriceBackward)
result.backward = testVariable %>% dplyr::select(Id,SalePrice)
write.csv(result.backward,"Backward_Prediction_Miller_YU.csv",row.names = FALSE)

#Try Mass Library Forward model - Same result 0.15432
backward.model2 = stepAIC(backward_fit,direction="backward")
backward.model2

#Testing with Mass Library
testVariable$lSalePriceBackward = predict(backward.model2,testVariable)
testVariable$SalePrice = exp(testVariable$lSalePriceBackward)
result.backward = testVariable %>% dplyr::select(Id,SalePrice)
write.csv(result.backward,"Backward_Prediction_2_Miller_YU.csv",row.names = FALSE)
```

### Backward Selection - use p-value - Kaggle 0.15505
```{r}
set.seed(16)
#create forward fit model

#write a program to pretict 20 different combination to test forward selection model
iterations = 20
splitPerc = 0.95
total_RMSE = 0
for(i in 1:iterations){
  print(i)
  trainIndices = sample(1:dim(variables.used)[1],round(splitPerc * dim(variables.used)[1]))
  train = variables.used[trainIndices,]
  test = variables.used[-trainIndices,]
  backward_fit = lm(lSalePrice~.-Id,data=train)
  backward.model = ols_step_backward_p(backward_fit,prem=0.1,details=FALSE)
  prediction = predict(backward.model$model,test)
  squared_MSPE = mean((test$lSalePrice - prediction)^2)
  temp_RMSE = sqrt(squared_MSPE)
  total_RMSE = total_RMSE+temp_RMSE
}
#CV Press estimate = 0.1306067
total_RMSE/iterations
#Build model with full dataset for fitting
backward_fit = lm(lSalePrice~.-Id,data=variables.used)
backward.model = ols_step_backward_p(backward_fit,prem=0.1,details=FALSE)
backward.model$model
backward.model
ols_plot_resid_stand(backward.model$model)
ols_plot_cooksd_bar(backward.model$model)
plot(backward.model$model)

testVariable$lSalePriceBackward = predict(backward.model$model,testVariable)
testVariable$SalePrice = exp(testVariable$lSalePriceBackward)
result.backward = testVariable %>% dplyr::select(Id,SalePrice)
write.csv(result.backward,"Backward_Prediction_usingP_Miller_YU.csv",row.names = FALSE)
```
